---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AmesA

<!-- badges: start -->
<!-- badges: end -->

The goal of AmesA is to summarize measured plant anatomical data and use it to estimate the surface area and volume of common types of mesophyll cells, the mesophyll airspace fraction, and the mesophyll surface area per leaf area. 

## Installation

You can install the development version of AmesA from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("a-lippert/AmesA")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(AmesA)
## basic example code
```

Suggested data structure: EASF=estimated airspace fraction; LT=leaf thickness; ET=epidermal thickness; MT=mesophyll thickness; SA=area of chunk of spongey mesophyll tissue; IAS=total area of intracellular airspace within above chunk of spongey mesophyll tissue

```{r cars}
print(DATASET)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
